Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-09 ms/main.tex
Handle Corollary 5 - derivative by T_B - fix

This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
However, increasing the horizontal transmission of defection can either increase or decrease the boundary, making it easier or harder for cooperation to evolve, respectively, depending if $T_A$ is high or low (i.e. if $T_A>1/(1+bv\alpha)$ or below).
% TODO write sign(dgamma1/dTB) = sign(???)
%TODO I think the boundary on TA should be (2TB-1)/(alpha*b*v+1). DC

>>>>

This condition merges the conditions for fixation of cooperation and for stable coexistence, which both lead to the instability of $\hat{p}=0$, the fixation of defection.
Importantly, increasing social association $\alpha$ increases the boundary cost ($\partial \hat\gamma_1 / \partial \alpha > 0$), making it easier for cooperation to increase from rarity.
Similarly, increasing the horizontal transmission of cooperation increases the boundary ($\partial \hat\gamma_1 / \partial T_A > 0$), making it easier for cooperation to evolve.
However, increasing the horizontal transmission of defection can either increase or decrease the boundary depending on $sign(\partial\gamma_1/\partial T_B) = sign(vb \alpha T_A+T_A-1)$. 
Therefore, increasing $T_B$ increases the boundary when $T_A > \frac{1}{1+\alpha b v}$ but when this applies we get that $\hat\gamma_1 > 1$ which guarantees cooperation will evolve from rairty since $c<1$.
When $T_A < \frac{1}{1+\alpha b v}$ increasing $T_B$ decreases the boundary.
